Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-14 thesis/chapters/ch_introduction.tex
Some slight rewording. Added intro to feedback section. Added supernova section cleaned up a bit of the radiation section. added stellar winds section. Feedback draft should be complete.

\subsubsection{Stellar Radiation Feedback}
\label{intro:sec:radiation}

@@

%
%
%
%\section{Semi-Analytic Models / One-zone Models}
%
%Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
%
%

>>>>

The first models of galacitc evolution produced galaxies with stellar masses far in excess of what is observed in the Universe, converting a substantial fraction of their baryons into stars. From these initial works, it was clear that some form of feedback process must take place to self-regulate star formation within galaxies. With observations of metal abundances in the CGM around galaxies \citep[see][ for a recent review]{Tumlinson2017}, and of fast-moving outflows from star forming galxaies \citep[see][ for a review]{Veilleux2005}, it was additionally clear that some mechanism must exist to drive these outflows. Stellar feedback became the clear physical mechanism to account for both of these phenomena.\footnote{Except maybe for more massive galaxies, where active galactic nuclei likely plan some role in regulating star formation and certainly play a role in driving outflows \citep[e.g.][]{Fabian2012}.}

Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:supernovae}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution). Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties, and includes stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).

Although not included in this dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution. A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references). In brief, cosmic rays can be a dominant source of heading in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}. In addition, binarity is often ignored in models of stellar feedback, but can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations, typically increasing their total energy output and decreasing the typical ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}). Finally, exoctic sources of stellar feedback, such as hupernovae, high-mass X-ray binaries, and neutron star neutron star mergers can also be a potentially important source of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}. However, the uncertainties in the frequency and delay time distributions for when these events should occur, and there relative rarity preclude including these effects in this dissertation.

\subsubsection{Supernova Feedback}
\label{intro:sec:supernovae}

In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion. In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case. The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events. This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lessim 10^5$~K, as opposed to $T > 10^7$~K, or so). This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy. This is still a problem today in large-box simulations of cosmological volumes which have insufficient resulution to resolve individual SNe. While some of the initial, ad-hoc fixes for this problem (e.g. turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{Hopkins2014,Simpson2015,Hopkins2018}.

High resolution simulations, like those developed in this dissertation, can typically resort to utilizing pure thermal energy injection into the fluid elements surrounding the supernova site and avoiding artificial ``overcooling". This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}. However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective. In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}. Including these physics, as discussed below, greatly reduces the typical ISM densities in which SNe occur, greatly increasing the likelihood that these events are well resolved.

\subsubsection{Stellar Radiation}
\label{intro:sec:radiation}

@@

\subsubsection{Stellar Winds}
\label{intro:sec:stellarwinds}

Stellar winds, in addition to stellar radiation, are a potentially important source of pre-SN feedback that helps regulate star formation in / around the birth clouds of newly formed stars. However, the hot ($T>10^{6}$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) winds from massive stars \citep{Weaver1977} are challenging to model self-consistently in galaxy-scale simulations. For this reason, there has been comparatively little research on how they affect global galaxy properties, even though some models do include their energy injection in an integrated / approximate fashion \citep[e.g.][]{FIRE}. However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment. For these reasons we do include a simplified model for stellar wind feedback in this disseration.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored. It is thus likely subdominant to radiation feedback.}
%
%
%
%\section{Semi-Analytic Models / One-zone Models}
%
%Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
%
%
